Automatic Matching of Bullet Lands

### 2017-06-23 imaging-paper.Rnw
Update reviewer response

\linenumbers
%\tableofcontents
%\newpage
<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
imgdir <- "Figure/"
codedir <- "code"
datadir <- "/Users/heike/papers/dissertations/eric-dissertation/images/Hamby (2009) Barrel/bullets/"
#datadir <- "images/Hamby (2009) Barrel/bullets"

>>>>

\linenumbers
%\tableofcontents
%\newpage
<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
imgdir <- "Figure/"
codedir <- "code"
datadir <- "images/Hamby (2009) Barrel/bullets"
